Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-12 content/appendix.tex
working on proofs

Finally, we present the proof for Lemma~\ref{lem:onlycorrec} which states that a correlated-calls analysis that considers all receivers computes the same result as an analysis that considers only correlated-call receivers.

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:onlycorrrec}}]
  From~\eqref{eq:ucc} we know that
  \begin{align*}
    \backCC(\resultIDE\left(\transCC_R(P)\right))
    &=\left\{(n,\,D_n^\Subset(\resultIDE(\transCC_R(P))))\ |\ n\in N^*\right\}.
  \end{align*}
  According to~\eqref{eq:dnq} and~Lemma~\ref{lem:recindep}, for a given $n\in N^*$,
  \begin{align*}
    D_n^\Subset&(\resultIDE(\transCC_R(P))))\\
    &=\left\{d\ |\ d\in\mvp F(n)\,\wedge\,\forall r\in R:\ \left\{(r,\,\resultIDE(\transCC_{\{r\}}(P))(n,\,d)(r))\ |\ r\in R\right\}(r)\ne\top_T\right\}\\
    &=\left\{d\ |\ d\in\mvp F(n)\,\wedge\,\forall\bm{r\in R}:\ \resultIDE(\transCC_{\{r\}}(P))(n,\,d)(r)\ne\top_T\right\}.
  \end{align*}

>>>>

Finally, we present the proof for Lemma~\ref{lem:onlycorrrec} which states that a correlated-calls analysis that considers all receivers computes the same result as an analysis that considers only correlated-call receivers.

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:onlycorrrec}}]
  From Section~\ref{sec:ideToIfds} we know that
  \[
    \backCC(\resultIDE\left(\transCC_R(P)\right))
    =\lambda n.\{d\,|\,\resultIDE(\transCC_R(P))(n)=(d,\,\ell),\,\forall r\,.\,\ell(r)\ne\topcc\}\,.
  \]
  We can rewrite this equation as follows:
  \[
    \backCC(\resultIDE\left(\transCC_R(P)\right))
    =\lambda n.\{d\,|\,\forall r,\,\resultIDE(\transCC_R(P))(n)=(d,\,\ell),\,\forall r\,.\,\ell(r)\ne\topcc\}\,.
  \]

  \begin{align*}
    \backCC(\resultIDE\left(\transCC_R(P)\right))
    &=\left\{(n,\,D_n^\Subset(\resultIDE(\transCC_R(P))))\ |\ n\in N^*\right\}.
  \end{align*}
  According to~\eqref{eq:dnq} and~Lemma~\ref{lem:recindep}, for a given $n\in N^*$,
  \begin{align*}
    D_n^\Subset&(\resultIDE(\transCC_R(P))))\\
    &=\left\{d\ |\ d\in\mvp F(n)\,\wedge\,\forall r\in R:\ \left\{(r,\,\resultIDE(\transCC_{\{r\}}(P))(n,\,d)(r))\ |\ r\in R\right\}(r)\ne\top_T\right\}\\
    &=\left\{d\ |\ d\in\mvp F(n)\,\wedge\,\forall\bm{r\in R}:\ \resultIDE(\transCC_{\{r\}}(P))(n,\,d)(r)\ne\top_T\right\}.
  \end{align*}

### 2014-12-12 content/impl.tex
addressing comments
working on proofs

Recall that in the equivalence transformation lattice $L^\equiv$, $\bot$ means reachable
and $\top$ means unreachable. Therefore, a result $\rho$ of the equivalence IDE analysis
is converted to an IFDS result as follows:
$\backEq(\rho) = \lambda n.\{d\mid\rho(n) = (d,\top)\}$.

>>>>

Recall that in the equivalence transformation lattice $L^\equiv$, $\bot$ means reachable
and $\top$ means unreachable.
\mtodo{Should it be $\topcc$ and $\botcc$?}
Therefore, a result $\rho$ of the equivalence IDE analysis
is converted to an IFDS result as follows:
$\backEq(\rho) = \lambda n.\{d\mid\rho(n) = (d,\top)\}$.
